Capstone Movielens Report

### 2025-05-23 reports/capstone-movielens.site/01.intro.Rmd
`UMGE Model: Support Funcions` section added.

Further analysis of the `edx` dataset have been also inspired by the article mentioned above[@MRS-R-BEST], from which the code and explanatory notes below were cited.
\newpage

@@

#### Ratings per movie
\
##### Movie popularity count[@MRS-R-BEST]
\
```{r}
print(edx |> 
  group_by(movieId) |> 
  summarize(count = n()) |>
  slice_head(n = 10)
)
```

>>>>

::: {.noteblock data-latex=""}
Further analysis of the `edx` dataset was also inspired by the article [Movie Recommendation System using R - BEST](https://www.kaggle.com/code/amirmotefaker/movie-recommendation-system-using-r-best/notebook) written by [Amir Moterfaker](https://www.kaggle.com/amirmotefaker)[@MRS-R-BEST], from which the code and explanatory notes below were cited.
:::

\newpage

@@

#### Ratings per movie
\

##### Movie popularity count[@MRS-R-BEST]
\
```{r}
print(edx |> 
  group_by(movieId) |> 
  summarize(count = n()) |>
  slice_head(n = 10)
)
```
